Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-05-20 main_paper.tex
[#7] Add number of replications used in naive bootstrap to the paper.
The number of replications was missing; this commit adds it.

Closes #7.

We include several other procedures for comparison: CCT's bias-corrected
interval using two different kernels, a ``naive'' uncorrected estimator, and
a bootstrapped version of the naive estimator.
We estimate CCT's bias corrected procedure with AMSE-optimal bandwidths for both
the uniform kernel and the triangular kernel. The uniform kernel provides a
direct comparison with our bootstrap, while the triangular kernel may be more
appealing to practitioners. The ``naive'' uncorrected interval
estimator uses the uniform kernel, again with the optimal bandwidth $h$ proposed by
\cite{IK}. And for the naive bootstrapped interval, we resample the data with
equal weights, find optimal bandwidth for each bootstrapped sample and calculate
the uncorrected point estimate. The $0.025$ and $0.975$ quantiles of the bootstrap
distribution are used as the lower and upper bound of the confidence interval.

>>>>

We include several other procedures for comparison: CCT's bias-corrected
interval using two different kernels, a ``naive'' uncorrected estimator and
a bootstrapped version of the naive estimator, using 999 bootstrap replications.
We estimate CCT's bias corrected procedure with AMSE-optimal bandwidths for both
the uniform kernel and the triangular kernel. The uniform kernel provides a
direct comparison with our bootstrap, while the triangular kernel may be more
appealing to practitioners. The ``naive'' uncorrected interval
estimator uses the uniform kernel, again with the optimal bandwidth $h$ proposed by
\cite{IK}. And for the naive bootstrapped interval, we resample the data with
equal weights, find optimal bandwidth for each bootstrapped sample and calculate
the uncorrected point estimate. The $0.025$ and $0.975$ quantiles of the bootstrap
distribution are used as the lower and upper bound of the confidence interval.
